Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 casestudies.tex
nits

LDAVis itself was developed by two members of the technical staff at
AT\&T Labs, and originally targeted RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides unparalleled ease of
development, discoverability and deployment turns out to be equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}).  On these aspects, RCloud provides a
very simple model: \emph{all developed notebooks are automatically
  deployed}.

@@

This application is simple, but highlights some of the unique features
of RCloud. While RCloud notebooks allow deployment of R analyses over
the web with no additional effor, RCloud \emph{applications} are more
powerful, and are developed in a combination of Javascript and HTML
for the front end. This requires additional knowledge than Shiny, but
we argue that the RCloud model makes the analysis side simpler for the
analysts (since they simply write the R code in the style they are
used to), and the front-end visualization side simpler for the
front-end developers (since they simply write the Javascript code in
the style \emph{they} are used to). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
regular RCloud notebooks.

>>>>

LDAVis itself was developed by two members of the technical staff at
AT\&T Labs, and originally targeted RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides unparalleled ease of
development, discoverability and deployment turn out to be equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}).  On these aspects, RCloud provides a
very simple model: \emph{all developed notebooks are automatically
  deployed}.

@@

This application is simple, but highlights some of the unique features
of RCloud. While RCloud notebooks allow deployment of R analyses over
the web with no additional effort, RCloud \emph{applications} are more
powerful, and are developed in a combination of Javascript and HTML
for the front end. This requires additional knowledge over Shiny, but
we argue that the RCloud model makes the analysis side simpler for the
analysts (since they simply write the R code in the style they are
used to), and the front-end visualization side simpler for the
front-end developers (since they simply write the Javascript code in
the style \emph{they} are used to). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
regular RCloud notebooks.
